A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-09-17 Manuscript/PNAS-Adams-Submitted.Rmd
empirical update

To demonstrate the utility of $\hat{Z}_{12}$, we compared  $Z_K$ for two ecologically-relevant traits in plethodontid salamander (Fig. 4): surface area to volume ratios (SA:V) and relative body width ($\frac{BW}{SVL}$) [@Baken2019; @Baken2020]. While both traits contained significant phylogenetic signal, tests based on $\hat{Z}_{12}$ revealed that the degree of phylogenetic signal was significantly stronger in SA:V ($\hat{Z}_{12}=4.13$; $P=0.000036$: Fig. 4). Biologically, this observation may be interpreted by the fact that the tropical species -- which form a monophyletic group within plethodontids -- display greater variation in SA:V, which covaries with disparity in their climatic niches [@Baken2020]. Thus, greater phylogenetic signal in SA:V is to be expected.

>>>>

To demonstrate the utility of $\hat{Z}_{12}$, we compared  $Z_K$ for two ecologically-relevant traits in plethodontid salamander (Fig. 4): surface area to volume ratios (SA:V) and relative body width ($\frac{BW}{SVL}$) [@Baken2019; @Baken2020]. While both traits contained significant phylogenetic signal, tests based on $\hat{Z}_{12}$ revealed that the degree of phylogenetic signal was significantly stronger in SA:V ($\hat{Z}_{12}=16.51$; $P< 0.00001$: Fig. 4). Biologically, this observation may be interpreted by the fact that the tropical species -- which form a monophyletic group within plethodontids -- display greater variation in SA:V, which covaries with disparity in their climatic niches [@Baken2020]. Thus, greater phylogenetic signal in SA:V is to be expected.
